---
title: "Supplementary Information - Paper Title"
format: html
---

Authors: Isabella C. Richmond^1^\*, Kayleigh Hutt-Taylor^1,2^, Lauren Bianco^1^, Antonia Vieira Zanella^3^, François Bérubé^4^, Paola Faddoul^4^, Kelly Vu^4^, Étienne Perreault-Mandeville^5^, Patrick Boivin^6^, Danielle Dagenais^6^, Nathalie Boucher^5^, Thi Thanh Hiên Pham^4^, Carly D. Ziter^1^

1 Department of Biology, Concordia University, Montreal Canada, H4B 1R6

2 Tree Canada

3 Department of Geography, Federal University of Paraná, Paraná Brazil,

4 Département d'études urbaines et touristiques, Université du Québec à Montréal, Montreal Canada,

5 Organisme Respire

6 École d'urbanisme et d'architecture de paysage, Université de Montréal, Montreal Canada

\* isabella.richmond\@mail.concordia.ca

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: setup

source('R/packages.R')

plot_prior <- function(mod, xmin, xmax, ylab){
  
  # how to sequence data
  seq_d <- seq(xmin, xmax, by = 0.5)
  
  # pull variables from model 
  vars <- colnames(mod$data)[-1]
  
  # identify categorical variables 
  factors <- names(Filter(is.factor,mod$data[-1]))
  
  # identify numeric variables 
  numeric <- names(Filter(is.numeric,mod$data[-1]))
  
  figlist <- lapply(numeric, function(x){
    
    df <- data.frame(matrix(ncol=length(vars),nrow=0, dimnames=list(NULL, vars)))
    
    df %<>%
      summarise_at(x, ~seq_d) %>%
      bind_rows(df, .) %>%
      mutate(across(all_of(factors), as.factor)) %>% 
      mutate(across(all_of(numeric), ~ replace(., is.na(.), 0)))
    
    epred <- add_epred_draws(df, mod)
    
    ggplot(epred, aes(x = get(x), y = .epred)) +
      geom_line(aes(group = .draw), alpha = 0.1) +
      labs(y = ylab, x = x) +
      theme_classic()
    
  })
}


plot_model <- function(model){
    
    # basic model fit plots
    plot(model)
  
    # Gelman plot
    ac <- as_draws_df(model) %>% 
      mutate(chain = .chain) %>% 
      mcmc_acf(pars = vars(b_Intercept), lags = 35)
    
    plot(ac)
  
    coda::gelman.plot(as.mcmc(model)[, "b_Intercept", ])
  
    # posterior check
    plot(pp_check(model, ndraws = 100))
  }


```




## Tables 

Table S1. Site characteristics. Infrastructure ID is the unique ID assigned to each individual site, where CON indicates a grey alley, RV indicates a green alley, and SS indicates a street segment. Parallel street names one of the parallel streets to each alley, and for street segments it indicates the street segment that was sampled for each alley. City is where the sampling occurred, VSMPE = Villeray-Saint Michel-Parc Extension and TR = Trois-Rivières. Infrastructure type indicates the site type, with three potential options, green alley, grey alley, and street segment. Percent canopy indicates the percent canopy of the site in decimal form. Firefly presence is a binomial variable, where 1 indicates that fireflies were found, 0 indicates no fireflies were found, and a blank indicates that the site was not sampled for fireflies. Number of points is the number of points where vegetative complexity was sampled (i.e., number of 10 m intervals).

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: table-s1

tar_load(ecological_benefits)

strts <- read.csv('input/parallel-streets.csv', encoding = 'UTF-8') %>% 
  mutate(street_segments = str_replace_all(InfrastructureID, c('CON-TR' = 'CON-SS-TR', 'CON-VSMPE' = 'CON-SS-VSMPE', 'RV-TR' ='RV-SS-TR', 'RV-VSMPE' = 'SS-VSMPE'))) %>% 
  pivot_longer(cols = c(InfrastructureID, street_segments), values_to = 'InfrastructureID') %>% 
  select(-name)



ecological_benefits %>% 
  inner_join(., strts) %>%
  select(c(InfrastructureID, parallel_street, city, type, per_can, firefly_presence, npoints)) %>% 
  mutate(type = case_when(type == 'Segments des Rues' ~ 'street segment',
                          type == 'Ruelles Vertes' ~ 'green alley',
                          type == 'Ruelles Traditionelles' ~ 'grey alley'),
         city = case_when(city == 'Villeray-Saint Michel-Parc Extension' ~ 'VSMPE',
                          city == 'Trois-Rivières' ~ 'TR')) %>% 
  st_drop_geometry() %>% 
  flextable() %>% 
  set_header_labels(
    InfrastructureID = "Infrastructure ID",
    parallel_street = "Parallel Street",
    city = "City",
    type = "Infrastructure Type",
    per_can = "Percent Canopy",
    firefly_presence = "Firefly Presence",
    npoints = "Number of Points"
  ) %>% 
  colformat_double(j = 'per_can', digits=2)


```



Table S2. Tree species characteristics 

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: table-s2




```









## Figures 


Figure S1. DAGS 



Figure S2. Mathstats notation for my models 




# Prior Predictive Checks 

Prior predictive checks are used to ensure that the values selected for priors for our models allow a biologically reasonable range of values. For numeric predictor variables, we simulate predictive draws for prior only models and visualize the slope/intercept of the values. We then do a "posterior predictive check" but with the prior only model, to see if the data is captured in the priors. Note that all data is scaled and centered in these data.

For Trois-Rivieres, there is only a categorical predictor variable. Therefore, only the posterior predictive check is presented.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: prior-setup


tar_load(prior_model_list)

vsmpe <- prior_model_list[grepl("vsmpe", names(prior_model_list))] %>% 
  setNames(., c('Canopy Cover', 'Firefly Abundance', 'Species Richness', 'Functional Diversity', 'Vertical Complexity', 
                'Percent Native', 'Percent Invasive', 'Temperature', 'Tree Abundance', 'Tree Size (DBH)', 'Tree Height', 'Percent Flowery'))
tr <- prior_model_list[grepl("tr", names(prior_model_list))] %>% 
  setNames(., c('Canopy Cover', 'Species Richness', 'Functional Diversity', 'Vertical Complexity', 
                'Percent Native', 'Percent Invasive', 'Temperature', 'Tree Abundance', 'Tree Size (DBH)', 'Tree Height', 'Percent Flowery'))

```


## Villeray-Saint Michel-Parc Extension
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: prior-plots-vsmpe


invisible(capture.output(lapply(seq_along(vsmpe), function(x){
  
  figs <- plot_prior(vsmpe[[x]], -3, 3, paste(names(vsmpe[x])))
  
  wrap_plots(figs, nrow = 2, ncol = 2) / pp_check(vsmpe[[x]], ndraws = 100) + 
    plot_layout(nrow = 2) + 
    plot_annotation(title = print(names(vsmpe[x])))
  
})))
```

## Trois-Rivieres
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: prior-plots-tr


invisible(capture.output(lapply(seq_along(tr), function(x){
  
  pp_check(tr[[x]], ndraws = 100) + 
    plot_annotation(title = print(names(tr[x])))
  
})))

```


# Model Diagnostics 

These model diagnostic plots assess whether the chains of our models are converged and well mixed, and if the model is well specified and has an adequate fit.

The first plot of the series shows trace plots for each of our parameters, where we want to see stationary and well-mixed chains. The second plot shows an autocorrelation plot by chain and parameter. We want our autocorrelation to quickly drop to zero with increasing lag. Thirdly, the Gelman plot indicates if the chains converge, where we want the value to decrease by the end of runtime. Finally, we have the posterior predictive check where we want the black line to be within/close to the blue lines, to indicate that our model is adequately generative.


```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: diagnostics-setup


tar_load(model_list)

vsmpe <- model_list[grepl("vsmpe", names(model_list))] %>% 
  setNames(., c('Canopy Cover', 'Firefly Abundance', 'Species Richness', 'Functional Diversity', 'Vertical Complexity', 
                'Percent Native', 'Percent Invasive', 'Temperature', 'Tree Abundance', 'Tree Size (DBH)', 'Tree Height', 'Percent Flowery'))

tr <- model_list[grepl("tr", names(model_list))] %>% 
  setNames(., c('Canopy Cover', 'Species Richness', 'Functional Diversity', 'Vertical Complexity', 
                'Percent Native', 'Percent Invasive', 'Temperature', 'Tree Abundance', 'Tree Size (DBH)', 'Tree Height', 'Percent Flowery'))


```



## Villeray-Saint Michel-Parc Extension
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: diagnostic-plots-vsmpe


invisible(capture.output(lapply(seq_along(vsmpe), function(x){
  
  plot_model(vsmpe[[x]]) + 
    plot_annotation(title = print(names(vsmpe[x])))
  
})))
```

## Trois-Rivieres
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: diagnostic-plots-tr

invisible(capture.output(lapply(seq_along(tr), function(x){
  
  plot_model(tr[[x]]) 
    plot_annotation(title = print(names(tr[x])))
  
})))

```