---
title: "Title: "
format: html
---

Authors: Isabella C. Richmond^1^\*, Kayleigh Hutt-Taylor^1,2^, Lauren Bianco^1^, Antonia Vieira Zanella^3^, François Bérubé^4^, Paola Faddoul^4^, Kelly Vu^4^, Étienne Perreault-Mandeville^5^, Patrick Boivin^6^, Danielle Dagenais^6^, Nathalie Boucher^5^, Thi Thanh Hiên Pham^4^, Carly D. Ziter^1^

1 Department of Biology, Concordia University, Montreal Canada, H4B 1R6

2 Tree Canada

3 Department of Geography, Federal University of Paraná, Paraná Brazil,

4 Département d'études urbaines et touristiques, Université du Québec à Montréal, Montreal Canada,

5 Organisme Respire

6 École d'urbanisme et d'architecture de paysage, Université de Montréal, Montreal Canada

\* isabella.richmond\@mail.concordia.ca

```{r, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
source('R/packages.R')

model_list <- tar_read(model_list)

plot_model <- function(model){
    
    # basic model fit plots
    plot(model)
  
    # Gelman plot
    ac <- as_draws_df(model) %>% 
      mutate(chain = .chain) %>% 
      mcmc_acf(pars = vars(b_Intercept), lags = 35)
    
    plot(ac)
  
    coda::gelman.plot(as.mcmc(model)[, "b_Intercept", ])
  
    # posterior check
    plot(pp_check(model, ndraws = 100))
  }
```

## Model Diagnostic Plots

These model diagnostic plots assess whether the chains of our models are converged and well mixed, and if the model is well specified and has an adequate fit.

The first plot of the series shows trace plots for each of our parameters, where we want to see stationary and well-mixed chains. The second plot shows an autocorrelation plot by chain and parameter. We want our autocorrelation to quickly drop to zero with increasing lag. Thirdly, the Gelman plot indicates if the chains converge, where we want the value to decrease by the end of runtime. Finally, we have the posterior predictive check where we want the black line to be within/close to the blue lines, to indicate that our model is adequately generative.

## Model 1a: Effect of Ruelle Type on Canopy Cover in Villeray-Saint Michel-Parc Extension (VSMPE)

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
mod <- model_list['canopy_vsmpe']
plot_model(mod[[1]])
```

## Model 1b: Effect of Ruelle Type on Canopy Cover in Trois-Rivieres (TR)

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
mod <- model_list['canopy_tr']
plot_model(mod[[1]])
```

